---
title: "Data Dictionary"
author: "Elsie Horne"
date: "08/09/2019"
output: rmarkdown::github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE,
                      fig.path = "data_dictionary_figs/")
library(tidyverse)
library(knitr)
library(kableExtra)
load("extract.RData")
```

The following table contains the names of all items for which data were extracted, along with a short description. Items are grouped according to the step of cluster analysis.  

Some items take values yes/no, e.g. 'Was the study identified in the PubMed search?'

* yes = it was identified
* no = it was not identified

Some items take values yes/no/NA, e.g. 'Were smokers excluded?'

* yes = the article states that smokers were excluded
* no = the article states that smokers were not excluded
* NA = the article does not mention whether smokers were excluded

Some items take the values yes/NA, e.g. 'Complete case analysis'

* yes = the article states that a complete case analysis was carried out
* NA = the article does not mention a complete case analysis (but we cannot categorically say that it was not as this may just be poor reporting)

```{r data_dictionary, include = FALSE}
data_dictionary <- tribble(
  ~`Item group`, ~`Item name`, ~`Description of item`,
  "General study information","author", "First author on study",
  "","year", "Year of publication",
  "","journal", "Publication journal",
  "","id", "Unique study ID",
  "","pubmed", "Was the study identified in the PubMed search? yes/no",
  "","scopus", "Was the study identified in the Scopus search? yes/no",
  "","date_extract", "Date of extraction",
  "","population", "Study population used in the cluster analysis",
  "","country", "Country of origin of study population",
  #####
  "Details regarding exclusion criteria","exc_smoke", "Were smokers were excluded? yes/no/NA",
  "","exc_copd", "Were patients with Chronic Obstructive Pulmonary Disease (COPD) were excluded? yes/no/NA",
  #####
  "Methods for chosing candidate cluster features","clinical_easy", "Were candidate cluster features chosen on the basis of being easy to measure in clinical practice? yes/NA",
  "","clinical_previous", "Were candidate cluster features chosen on the basis of previous studies? yes/NA",
  "","clinical_redundance", "Were candidate cluster features chosen on the basis of avoiding clinical redundancy? yes/NA",
  "","clinical_relevence", "Were candidate cluster features chosen on the basis of their relevance to asthma subtypes? yes/NA",
  #####
 "Method for dealing with missing data","miss_cc", "Complete case analysis: yes/NA",
 "","miss_handle", "Cluster analysis methods could handle missing data: yes/NA",
 "","miss_impute", "Imputation: yes/NA",
 "","miss_none", "No missing data present: yes/NA",
 "","miss_pat", "Patients with >x% missing data removed: yes/NA",
 "","miss_var", "Features with >x% missing values removed: yes/NA",
 #####
  "Patients included in cluster analysis", "n_pat", "Number of patients",
  #####
 "Univariate variable transformations","ut_box", "Box-cox power transformation: yes/NA",
 "","ut_log", "Log-transformation: yes/NA",
 "","ut_unclear", "Univariate feature transformation carried out but methods unclear: yes/NA",
 #####
 "Method of feature selection","vselect_coll", "Avoid collinearity: yes/NA",
 "","vselect_fa", "Factor analysis: yes/NA",
 "","vselect_mca", "Multiple correspondence analysis: yes/NA",
 "","vselect_multico", "Avoid multicollinearity: yes/NA",
 "","vselect_pca", "Principal component analysis: yes/NA",
 "","vselect_supervised", "On the basis of statistical tests: yes/NA",
 #####
   "Methods of feature transformation","ft_factor", "Factor analysis: yes/NA",
  "","ft_mca", "Multiple correspondence analysis: yes/NA",
  "","ft_pca", "Principal component analysis: yes/NA",
 #####
 "Cluster feature details", "data_type", "Type of cluster features: categorical/continuous/mixed/unclear",
 "", "n_cat_feat", "Number of categorical cluster features",
 "","n_cont_feat", "Number of continuous cluster features",
 "","n_feat", "Total number of cluster features",
 "", "encode_bin","Were all categorical variables encoded as binary variables: yes/NA",
 #####
 "Methods used to scale the features","scale_01", "Scaled to the range [0,1]: yes/NA",
 "","scale_aad", "Average absolute deviation: yes/NA",
 "","scale_centre", "Centre-scaled: yes/NA",
 "","scale_gower", "Gower standardisation: yes/NA",
 "","scale_unit", "Scaled to unit length: yes/NA",
 "","scale_unspec", "Standardised but method unspecified: yes/NA",
 "","scale_z", "z-scores: yes/NA",
 "","scale_z_one", "One feature scaled to z-scores: yes/NA",
 #####
 "Dissimilarity measure used","prox_euc_ass", "Euclidean assumed due to cluster analysis method: yes/NA",
 "","prox_euc_ex", "Euclidean stated: yes/NA",
 "","prox_gower", "Gower's coefficient: yes/NA",
 "","prox_ll_ass", "Log-likelihood measure assumed due to cluster analysis method: yes/NA",
 "","prox_ll_exp", "Log-likelihood measure stated: yes/NA",
 "","prox_spearman", "Dissimilarity measure based on Sprearman's Rho: yes/NA",
 "","prox_tree", "Tree-based method using the treeClust R package: yes/NA",
 #####
  "Methods of cluster analysis","cluster_fuzzypam", "Fuzzy Partition Around Medoids: yes/NA",
  "","cluster_hier", "Hierarchical clustering with no details of linkage: yes/NA",
  "","cluster_hier_ave", "Hierarchical clustering with average linkage: yes/NA",
  "","cluster_kmean", "k-means: yes/NA",
  "","cluster_kmean_ward", "k-means for pre-clusters, hierarchical with Ward's linkage for final clusters: yes/NA",
  "","cluster_kmedoid", "k-medoids: yes/NA",
  "","cluster_mmlmkkc", "Multiple kernel k-means: yes/NA",
  "","cluster_pre_hier", "Pre-clustering followed by hierarchical clustering: yes/NA",
  "","cluster_spec", "Spectral clustering: yes/NA",
  "","cluster_spss", "SPSS TwoStep: yes/NA",
  "","cluster_unclear", "Unclear clustering methods: yes/NA",
  "","cluster_ward", "Hierarchical clustering with Ward's linkage: yes/NA",
  #####
 "Method for choosing the number of clusters","k_bic", "Bayesian Information Criterion (Implemented as part of SPSS Two Step): yes/NA",
 "","k_dend", "Dendrogram (explicitly stated or diagram included, stating hierarchical techniques not sufficient): yes/NA",
 "","k_interp", "Clinical interpretation of the cluster solution: yes/NA",
 "","k_max", "Did the study specify the maximum number of clusters which they considered?: yes/NA",
 "","details_k_max", "What was the maximum number of clusters considered?",
 "","k_mpc", "Did the study state the minumum size of cluster which they accept? yes/NA",
 "","details_k_mpc", "What was the minimum size of cluster considered?",
 "","k_previous", "Previous studies/results: yes/NA",
 "","k_scree", "Scree plot: yes/NA",
 "","k_silhouette", "Silhouette plot: yes/NA",
 "","k_stat", "Statistic(s): yes/NA", 
 "","details_k_stat", "Which statistic(s) were used?",
 "","details_k_stat_n", "How many statistics were used?",
 "","k_unclear", "Unclear methods for choosing the  number of clusters: : yes/NA",
 "","k_wards", "Hierarchical clustering with Ward's linkage: yes/NA",
 "","n_k", "Number of clusters chosen",
 #####
 "Method for testing quality of clusters","rep_initial", "Repeat with different initial values: yes/NA",
 "","rep_method", "Repeat with different methods: yes/NA",
 "","rep_select", "Repeat in a selected subset: yes/NA",
 "","rep_sep", "Repeat in a separate cohort: yes/NA",
 "","rep_software", "Repeat with different software: yes/NA",
 "","rep_time", "Repeat at different time-point: yes/NA",
 "","rep_var", "Repeat with altered variables: yes/NA",
 #####
 "Method for testing the stability of the clusters","stab_boot", "Bootstrap methods: yes/NA",
 "","stab_loo", "Leave-one-out cross-validation: yes/NA",
 "","stab_random", "Repeat in random subset: yes/NA",
 "","stab_tt", "Split into train and test set: yes/NA",
 "","stab_unclear", "Methods unclear: yes/NA",
  #####
 "Reporting", "details_report_stab", "Were the results of testing the stability/quality of the solution reported: yes/no/NA",
 #####
 "Classification method using clusters as outcome", "class", "decision tree/stepwise discriminant analysis/linear discriminant analysis/multiclass  svm/discriminant analysis/boruta feature selection algorithm/classifier not specified/logistic regression/stepwise descriminant analysis and decision tree"
)
```

```{r create_table}
data_dictionary %>%
    kable(format = "markdown",
        booktabs = TRUE, 
        align = "l", 
        linesep = '',
        escape = FALSE)
```