---
title: "Data Dictionary"
author: "Elsie Horne"
date: "08/09/2019"
output: rmarkdown::github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
library(tidyverse)
library(knitr)
library(kableExtra)
load("extract.RData")
```

The following table contains the names of all items for which data were extracted, along with a short description. Items are grouped according to the step of cluster analysis.  

Some items take values yes/no, e.g. 'Was the study identified in the PubMed search?'

* yes = it was identified
* no = it was not identified

Some items take values yes/no/NA, e.g. 'Were smokers exluded?'

* yes = the article states that smokers were excluded
* no = the article states that smokers were not excluded
* NA = the article does not mention whether smokers were excluded

Some items take the values yes/NA, e.g. 'Complete case analysis'

* yes = the article states that a complete case analysis was carried out
* NA = the article does not mention a complete case analysis (but we cannot categorically say that it was not as this may just be poor reporting)

```{r data_dictionary, include = FALSE}
data_dictionary <- tribble(
  ~`Item group`, ~`Item name`, ~`Description of item`,
  "General study information","author", "First author on study",
  "General study information","year", "Year of publication",
  "General study information","journal", "Publication journal",
  "General study information","id", "Unique study ID",
  "General study information","pubmed", "Was the study identified in the PubMed search? yes/no",
  "General study information","scopus", "Was the study identified in the Scopus search? yes/no",
  "General study information","date_extract", "Date of extraction",
  "General study information","population", "Study population used in the cluster analysis",
  "General study information","country", "Country of origin of study population",
  #####
  "Details regarding exclusion criteria","exc_smoke", "Were smokers were excluded? yes/no/NA",
  "Details regarding exclusion criteria","exc_copd", "Were patients with Chronic Obstructive Pulmonary Disease (COPD) were excluded? yes/no/NA",
  #####
  "Methods for chosing candidate cluster features","clinical_easy", "Were candidate cluster features chosen on the basis of being easy to measure in clinical practice? yes/NA",
  "Methods for chosing candidate cluster features","clinical_previous", "Were candidate cluster features chosen on the basis of previous studies? yes/NA",
  "Methods for chosing candidate cluster features","clinical_redundance", "Were candidate cluster features chosen on the basis of avoiding clinical redundancy? yes/NA",
  "Methods for chosing candidate cluster features","clinical_relevence", "Were candidate cluster features chosen on the basis of their relevance to asthma subtypes? yes/NA",
  #####
   "Method for dealing with missing data","miss_cc", "Complete case analysis: yes/NA",
 "Method for dealing with missing data","miss_handle", "Cluster analysis methods could handle missing data: yes/NA",
 "Method for dealing with missing data","miss_impute", "Imputation: yes/NA",
 "Method for dealing with missing data","miss_none", "No missing data present: yes/NA",
 "Method for dealing with missing data","miss_pat", "Patients with >x% missing data removed: yes/NA",
 "Method for dealing with missing data","miss_var", "Features with >x% missing values removed: yes/NA",
 #####
  "Patients included in cluster analysis", "n_pat", "Number of patients",
  #####
 "Univariate variable transformations","ut_box", "Box-cox power transformation: yes/NA",
 "Univariate variable transformations","ut_log", "Log-transformation: yes/NA",
 "Univariate variable transformations","ut_unclear", "Univariate feature transformation carried out but methods unclear: yes/NA",
 #####
 "Method of feature selection","vselect_coll", "Avoid collinearity: yes/NA",
 "Method of feature selection","vselect_fa", "Factor analysis: yes/NA",
 "Method of feature selection","vselect_mca", "Multiple correspondence analysis: yes/NA",
 "Method of feature selection","vselect_multico", "Avoid multicollinearity: yes/NA",
 "Method of feature selection","vselect_pca", "Principal component analysis: yes/NA",
 "Method of feature selection","vselect_supervised", "On the basis of statistical tests: yes/NA",
 #####
   "Methods of feature transformation","ft_factor", "Factor analysis: yes/NA",
  "Methods of feature transformation","ft_mca", "Multiple correspondence analysis: yes/NA",
  "Methods of feature transformation","ft_pca", "Principal component analysis: yes/NA",
 #####
   "Cluster feature details", "data_type", "Type of cluster features: categorical/continuous/mixed/unclear",
   "Cluster feature details", "n_cat_feat", "Number of categorical cluster features",
 "Cluster feature details","n_cont_feat", "Number of continuous cluster features",
 "Cluster feature details","n_feat", "Total number of cluster features",
  "Cluster feature details", "encode_bin","Were all categorical variables encoded as binary variables: yes/NA",
 #####
 "Methods used to scale the features","scale_01", "Scaled to the range [0,1]: yes/NA",
 "Methods used to scale the features","scale_aad", "Average absolute deviation: yes/NA",
 "Methods used to scale the features","scale_centre", "Centre-scaled: yes/NA",
 "Methods used to scale the features","scale_gower", "Gower standardisation: yes/NA",
 "Methods used to scale the features","scale_unit", "Scaled to unit length: yes/NA",
 "Methods used to scale the features","scale_unspec", "Standardised but method unspecified: yes/NA",
 "Methods used to scale the features","scale_z", "z-scores: yes/NA",
 "Methods used to scale the features","scale_z_one", "One feature scaled to z-scores: yes/NA",
 #####
 "Dissimilarity measure used","prox_euc_ass", "Euclidean assumed due to cluster analysis method: yes/NA",
 "Dissimilarity measure used","prox_euc_ex", "Euclidean stated: yes/NA",
 "Dissimilarity measure used","prox_gower", "Gower's coefficient: yes/NA",
 "Dissimilarity measure used","prox_ll_ass", "Log-likelihood measure assumed due to cluster analysis method: yes/NA",
 "Dissimilarity measure used","prox_ll_exp", "Log-likelihood measure stated: yes/NA",
 "Dissimilarity measure used","prox_spearman", "Dissimilarity measure based on Sprearman's Rho: yes/NA",
 "Dissimilarity measure used","prox_tree", "Tree-based method using the treeClust R package: yes/NA",
 #####
  "Methods of cluster analysis","cluster_fuzzypam", "Fuzzy Partition Around Medoids: yes/NA",
  "Methods of cluster analysis","cluster_hier", "Hierarchical clustering with no details of linkage: yes/NA",
  "Methods of cluster analysis","cluster_hier_ave", "Hierarchical clustering with average linkage: yes/NA",
  "Methods of cluster analysis","cluster_kmean", "k-means: yes/NA",
  "Methods of cluster analysis","cluster_kmean_ward", "k-means for pre-clusters, hierarchical with Ward's linkage for final clusters: yes/NA",
  "Methods of cluster analysis","cluster_kmedoid", "k-medoids: yes/NA",
  "Methods of cluster analysis","cluster_mmlmkkc", "Multiple kernel k-means: yes/NA",
  "Methods of cluster analysis","cluster_pre_hier", "Pre-clustering followed by hierarchical clustering: yes/NA",
  "Methods of cluster analysis","cluster_spec", "Spectral clustering: yes/NA",
  "Methods of cluster analysis","cluster_spss", "SPSS TwoStep: yes/NA",
  "Methods of cluster analysis","cluster_unclear", "Unclear clustering methods: yes/NA",
  "Methods of cluster analysis","cluster_ward", "Hierarchical clustering with Ward's linkage: yes/NA",
  #####
 "Method for choosing the number of clusters","k_bic", "Bayesian Information Criterion (Implemented as part of SPSS Two Step): yes/NA",
 "Method for choosing the number of clusters","k_dend", "Dendrogram (explicitly stated or diagram included, stating hierarchical techniques not sufficient): yes/NA",
 "Method for choosing the number of clusters","k_interp", "Clinical interpretation of the cluster solution: yes/NA",
 "Method for choosing the number of clusters","k_max", "Did the study specify the maximum number of clusters which they considered?: yes/NA",
 "Method for choosing the number of clusters","details_k_max", "What was the maximum number of clusters considered?",
 "Method for choosing the number of clusters","k_mpc", "Did the study state the minumum size of cluster which they accept? yes/NA",
 "Method for choosing the number of clusters","details_k_mpc", "What was the minimum size of cluster considered?",
 "Method for choosing the number of clusters","k_previous", "Previous studies/results: yes/NA",
 "Method for choosing the number of clusters","k_scree", "Scree plot: yes/NA",
 "Method for choosing the number of clusters","k_silhouette", "Silhouette plot: yes/NA",
 "Method for choosing the number of clusters","k_stat", "Statistic(s): yes/NA", 
 "Method for choosing the number of clusters","details_k_stat", "Which statistic(s) were used?",
 "Method for choosing the number of clusters","details_k_stat_n", "How many statistics were used?",
 "Method for choosing the number of clusters","k_unclear", "Unclear methods for choosing the  number of clusters: : yes/NA",
 "Method for choosing the number of clusters","k_wards", "Hierarchical clustering with Ward's linkage: yes/NA",
 "Method for choosing the number of clusters","n_k", "Number of clusters chosen",
 #####
 "Method for testing quality of clusters","rep_initial", "Repeat with different initial values: yes/NA",
 "Method for testing quality of clusters","rep_method", "Repeat with different methods: yes/NA",
 "Method for testing quality of clusters","rep_select", "Repeat in a selected subset: yes/NA",
 "Method for testing quality of clusters","rep_sep", "Repeat in a separate cohort: yes/NA",
 "Method for testing quality of clusters","rep_software", "Repeat with different software: yes/NA",
 "Method for testing quality of clusters","rep_time", "Repeat at different time-point: yes/NA",
 "Method for testing quality of clusters","rep_var", "Repeat with altered variables: yes/NA",
 #####
 "Method for testing the stability of the clusters","stab_boot", "Bootstrap methods: yes/NA",
 "Method for testing the stability of the clusters","stab_loo", "Leave-one-out cross-validation: yes/NA",
 "Method for testing the stability of the clusters","stab_random", "Repeat in random subset: yes/NA",
 "Method for testing the stability of the clusters","stab_tt", "Split into train and test set: yes/NA",
 "Method for testing the stability of the clusters","stab_unclear", "Methods unclear: yes/NA",
  #####
 "Reporting", "details_report_stab", "Were the results of testing the stability/quality of the solution reported: yes/no"
)
```

```{r create_table}
data_dictionary %>%
    kable(format = "html",
        booktabs = TRUE, 
        align = "l", 
        linesep = '',
        escape = FALSE) %>% 
  kable_styling(bootstrap_options = c("condensed"), 
                  full_width = F,
                  position = "left") %>%
  collapse_rows(columns = 1, 
                row_group_label_position = 'stack')
```